Ground state energy of quantum dots using the coupled cluster method

### 2018-06-03 project_2/article/article.tex
Intermediates: think I have it now.

		\subsubsection{Intermediate Computations}
		Looking closely at the amplitude equation in (\ref{eq:CCD_amp_1}) one might come
		to realize that it contains that this equation contains many of the same structures in
		several of the terms. This warrants the search for an algebraic transformation of the
		CCD amplitude equation that has the potential to reduce the amount of floating point
		operations needed to compute it. As it turns out, such terms exist and they will decrease
		the computing time necessary by an order of magnitude. We will define the following
		"intermediates",
		\begin{align}
			 \chi^{ab}_{cd} &= \frac{1}{4}t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}u^{ab}_{cd} \\
    			 \chi^a_d &= \frac{1}{2} t^{ac}_{nm} u^{nm}_{cd} \\
   			 \chi^{bm}_{jc} &= u^{bm}_{jc} + \frac{1}{2}t^{bd}_{jn}u^{mn}_{cd} \\
    			 \chi^n_j &= \frac{1}{2}t^{cd}_{jm} u^{mn}_{cd}.
		\end{align}
		These intermediate structures will allow us to rewrite \autoref{eq:CCD_amp_1} to,
		THIS REMAINS TO BE CHECKED!! 
		\begin{equation}
		\begin{aligned}
			0 =& \frac{1}{2}t^{ab}_{mn}u^{mn}_{ij} - t^{ab}_{im}u^{mn}_{jn}P(ij)
      		+ t^{cd}_{ij}\chi^{ab}_{cd} + t^{ac}_{ij}\chi^b_c P(ab) \\
      	  &+ t^{ac}_{im}\chi^{bm}_{jc}P(ab)P(ij)
      		+ t^{ab}_{in}\chi^n_jP(ij) + u^{ab}_{ij}.
		\end{aligned}
		\end{equation}
		The importance of this "trick" will become apparent in due time.

>>>>

		\subsubsection{Intermediate Computations}
		Looking closely at the amplitude equation in (\ref{eq:CCD_amp_1}) one might come
		to realize that it contains that this equation contains many of the same structures in
		several of the terms. This warrants the search for an algebraic transformation of the
		CCD amplitude equation that has the potential to reduce the amount of floating point
		operations needed to compute it. As it turns out, such terms exist and they will decrease
		the computing time necessary by an order of magnitude. We will define the following
		"intermediates",
		\begin{align}
			 \chi^{ab}_{cd} &= \frac{1}{4}t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}u^{ab}_{cd} \\
    			 \chi^a_d &= \frac{1}{2} t^{ac}_{nm} u^{nm}_{cd} \\
   			 \chi^{bm}_{jc} &= u^{bm}_{jc} + \frac{1}{2}t^{bd}_{jn}u^{mn}_{cd} \\
    			 \chi^n_j &= \frac{1}{2}t^{cd}_{jm} u^{mn}_{cd}.
		\end{align}
		These intermediate structures will allow us to rewrite \autoref{eq:CCD_amp_1} to,
		THIS REMAINS TO BE CHECKED!! 
		\begin{equation}
		\begin{aligned}
			0 =& \frac{1}{2}t^{ab}_{mn}u^{mn}_{ij} - t^{ab}_{im}u^{mn}_{jn}P(ij)
      		+ t^{cd}_{ij}\chi^{ab}_{cd} - t^{bd}_{ij}\chi^a_d P(ab) \\
      	  &+ t^{ac}_{im}\chi^{bm}_{jc}P(ab)P(ij)
      		+ t^{ab}_{in}\chi^n_jP(ij) + u^{ab}_{ij}.
		\end{aligned}
		\end{equation}
		The importance of this "trick" will become apparent in due time.
